---
title: "Reproducible_Report"
author: "Rui"
date: "12 Dezember 2017"
output: 
 word_document:
   reference_docx: style.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is my Report

# Advantage 1: Consitent layout whatever you do
I can write stuff in **R-Markdown** and it will appear in Word with the Layout
I pre-defined in my style.docx. Very nice indeed. 
This means I can make sure that all documents I write have exactly the same layout because they all use the same style template. Set a layout once and you don't need to care about it anymore.

# Advantage 2: Easily including graphs/images/tables produced in R into your document
But that is only part of the beauty. I can also include all sorts of R code chunks, and easily include graphs and tables.

```{r cars}
summary(cars)
```

## Including Plots

```{r pressure, echo=FALSE}
plot(pressure)
```

# Advantage 3: Set global variables, pieces of text that you can re-use in the whole document.

You can use pre-defined variables in your text:

```{r}
email= "my_email@adress.com"
```

This is my `r email`

# Advantage 4: Combining advantage 3 with databases
If you combine this feature with an outside database, for example an excel sheet,
and let R loop trough the rows, including certain variables in the text, you can create several equal documents with content changing according to a database.

For example, if you have to write several letters to different people, this will
come in very handy. 

We can write one letter setting one set of values:

```{r}
Name= "Bob"
Status= "Famous"
Address= "Penny Lane"
```

To: `r Status` `r Name`           
Address: `r Address`

## Now lets write 3 letters to 3 customers at the same time:

For this we need to use an additional R file which will call this markdown file!

If we do not have this additional file, the next piece of code needs to be
commented out!


```{r}
#row=data[rownames(data)==i,]
#Name= row$Name
#Status= row$Status
#Address= row$Address
```

To: `r Status` `r Name`        
Address: `r Address`





